paper

### 2024-09-26 inst/extdata/paperdata/paper.qmd
.

limrots.result <- readRDS("paperdata/UPS1.Case0.LimROTS.rds")
rots.result <- readRDS("paperdata/UPS1.Case0.ROTS.rds")
limma.result <- readRDS("paperdata/UPS1.Case0.limma.rds")
t.test.result <- readRDS("paperdata/UPS1.Case0.t.test.rds")
samr.result <- readRDS("paperdata/UPS1.Case0.samr.rds")

@@

```{r}
# Load necessary packages
library(LimROTS)
library(parallel)
# Load the dataset
data("proteogenomicPD")
print(soma)

@@

# Set metadata and formula for LimROTS analysis
meta.info <- names(soma@colData@listData)[1:6]
B <- 1000  # Number of bootstrap samples
K <- dim(soma)[1]/2  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "group_comp"
formula.str <- "~ 0 + group_comp + gender + AGE + CNO + pc1 + pc2"  # Formula for group comparison
# Run LimROTS analysis with trend and robust settings enabled

@@

```{r}
library(limma)
library(SummarizedExperiment, quietly = T, warn.conflicts = T)
data("soma")
data <- assay(soma)
formula.str <- "~ 0 + group_comp + gender + AGE + CNO + pc1 + pc2 + pc3 + pc4"
meta.info <- data.frame(colData(soma), check.names = FALSE, row.names = row.names(colData(soma)))
meta.info$sample.id <- NULL
meta.info$CNO <- as.factor(meta.info$CNO)
design.matrix <- model.matrix(formula(formula.str), data = meta.info)
colnames(design.matrix) <- make.names(colnames(design.matrix))
fit <- lmFit(data, design.matrix)
cont_matrix <- makeContrasts("group_comp1-group_comp2",  levels=design.matrix)
fit2 <- contrasts.fit(fit, cont_matrix)
fit.ebayes <- eBayes(fit2, trend=TRUE, robust=TRUE)
limma.result <- topTable(fit.ebayes, coef="group_comp1-group_comp2" , number = "Inf")

@@

length(which(limma.result$adj.P.Val < 0.05))

>>>>

#limrots.result <- readRDS("paperdata/UPS1.Case0.LimROTS.rds")
rots.result <- readRDS("../../extdata/paperdata/UPS1.Case0.ROTS.rds")
limma.result <- readRDS("../../extdata/paperdata/UPS1.Case0.limma.rds")
t.test.result <- readRDS("../../extdata/paperdata/UPS1.Case0.t.test.rds")
samr.result <- readRDS("../../extdata/paperdata/UPS1.Case0.samr.rds")

@@

```{r}
# Load necessary packages
library(LimROTS)
library(parallel)
library(SummarizedExperiment)
# Load the dataset
data("proteogenomicPD")
print(soma)

@@

# Set metadata and formula for LimROTS analysis
meta.info <- names(soma@colData@listData)
B <- 2000  # Number of bootstrap samples
K <- dim(soma)[1]/2  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "group_comp"
formula.str <- "~ 0 + group_comp + gender + AGE + CNO + pc1 + pc2 + pc3 + pc4"  # Formula for group comparison
# Run LimROTS analysis with trend and robust settings enabled

@@

```{r}
library(limma)
library(SummarizedExperiment, quietly = T, warn.conflicts = T)

data <- assay(soma)
formula.str <- "~ 0 + group_comp + gender + AGE + CNO + pc1 + pc2 + pc3 + pc4"
meta.info <- data.frame(colData(soma), check.names = FALSE, row.names = row.names(colData(soma)))
meta.info$sample.id <- NULL
meta.info$CNO <- as.factor(meta.info$CNO)
design.matrix <- model.matrix(formula(formula.str), data = meta.info)
colnames(design.matrix) <- make.names(colnames(design.matrix))
fit <- lmFit(data, design.matrix)
cont_matrix <- makeContrasts("group_comp1-group_comp2",  levels=design.matrix)
fit2 <- contrasts.fit(fit, cont_matrix)
fit.ebayes <- eBayes(fit2, trend=TRUE, robust=TRUE)
limma.result <- topTable(fit.ebayes, coef="group_comp1-group_comp2" , number = "Inf")

@@

length(which(limma.result$adj.P.Val < 0.01))
